$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in the Presence of Non-Functional Properties

### 2013-12-13 JournalToSubmit2013/modelingFlyingPig.tex
no message

The e3value model is a static representation of a business case.
The model defines \textit{dependency paths}, which show that the value exchanges are triggered by the occurrence of an end-consumer need. 
A dependency path has a direction and consists of a sequence of linked nodes. 
A dependency node is a start stimulus, an AND-fork or AND-join, an OR-fork or OR-join, or an end node (see Legend on Figure~\ref{fig:E3valuemodel}). An start stimulus represents a trigger for the exchange of economic value objects while an end node represents a model boundary.

Besides the static representation of a business case, the value model allows for the representation of dependency paths which enhance the understanding of a business idea by showing all value exchanges triggered by the occurrence of an end-consumer need. A dependency path has a direction and consists of dependency nodes linked by mean of connections. A dependency node is a start stimulus, an AND-fork or AND-join, an OR-fork or OR-join, or an end node (see Legend on Figure~\ref{fig:E3valuemodel}). An start stimulus represents a trigger for the exchange of economic value objects while an end node represents a model boundary.

>>>>

The e3value model is a static representation of a business case.
The model defines \textit{dependency paths}, showing the value exchanges, which are triggered by the occurrence of an end-consumer need (in our case, the need of a risk assessment). 
A dependency path has a direction and consists of a sequence of linked dependency nodes.
A dependency path startr with a \textit{start stimulus} node and ends with an \textit{end stimulus} node (see Legend on Figure~\ref{fig:E3valuemodel}).

AQUI!!!
